Think deep for reef resilience

### 2025-09-25 paper/paper_draft.qmd
Note for @eco-ben

Analyses for source-to-sink ratio and incoming and outgoing connectivity metrics suggest
that reefs with greater outgoing connectivity and lower incoming connectivity levels have
higher probability of being clustered into the Low cover cluster compared to other reefs.
Additionally, two-way analyses revealed little interaction between depth and incoming and
outgoing connectivity metrics for reef clustering probabilities
(@fig-ts-cluster-pdp-twoway-incoming; @sfig-ts-cluster-pdp-twoway-outgoing). Reefs with a
median depth around 15m and high incoming connectivity may benefit slightly, with higher
probability of High cover cluster assignment compared to 15m - depth reefs with lower
connectivity.

>>>>

Analyses for source-to-sink ratio and incoming and outgoing connectivity metrics suggest
that reefs with greater outgoing connectivity and lower incoming connectivity levels have
higher probability of being clustered into the Low cover cluster compared to other reefs
**\[Ben, I disagree with this assessment and the next sentence seems to contradict it?\]**.
Additionally, two-way analyses revealed little interaction between depth and incoming and
outgoing connectivity metrics for reef clustering probabilities
(@fig-ts-cluster-pdp-twoway-incoming; @sfig-ts-cluster-pdp-twoway-outgoing). Reefs with a
median depth around 15m and high incoming connectivity may benefit slightly, with higher
probability of High cover cluster assignment compared to 15m - depth reefs with lower
connectivity.
